### 2019-05-13 thesis.tex
Rewriting the introduction
Started with de definition of plasma (still to be finished);

Next, talk about why studying plasma is important.

% LFZ180220: Coloquei espaço entre a vírgula e "Phys. Rev. E". E coloquei
% vírgula após "incorporated", na linha que segue.

@@

% LFZ180220: Mudei "outcomes" para "outcome", uma vez que o verbo está como
% "was".
% Sabrina: não seria melhor manter o "outcomes" e trocar "was" por "were"?
% É que tem mais de um resultado... Ou será que dá pra considerar esses
% dois itens como um resultado global?

@@

  damping rate for Langmuir and ion-sound waves, and the discovery of a
  new fundamental  process of emission of electrostatic fluctuations, in
  the ion-sound and Langmuir frequency range, caused by binary interactions
  of particles,
% LFZ180220: Não fica melhor "caused by binary interactions of particles",
% em lugar de "caused by particle scattering"? Se não achares adequado tens
% que voltar à forma anterior.
% Sabrina: Acho que pode ser. Na verdade meio que copiei parte dessa frase
% do artigo. Acho que o Peter quis dar ênfase ao fato de a mudança na forma
% da função de distribuição ser causada por espalhamento. Mas concordo que
% aqui pode causar certa confusão por causa do efeito de espalhamento das
% ondas. Então concordo, já fiz a mudança.
  named \emph{electrostatic bremsstrahlung}. In the present study we
  introduce the first numerical analysis of these two new equations and

@@

  %The first work concerns the collisional damping equation, where we compare

@@

  and in it we compare
% LFZ180220: Fiz uma proposta de mmudança na frase. OK?
% Sabrina: OK
  the results of numerical integration of the rigorous expression with the
  damping rate calculated with the widely applied \emph{Spitzer formula}.
  % Besides that, the insignificance of the collisional damping rate gets
  % LFZ180220: Aqui também, proposta de mudança na frase. Entre outras coisas,
% estou propondo inversão das frases. OK?
% (verifiquei que essa nova ordem está de acordo com o que estava no resumo,
% abaixo)
% Sabrina: ah sim, a ideia de inserir essa frase veio quando eu estava
% escrevendo o resumo já, aí só acrescentei aqui, mas no lugar errado,
% pelo visto
  We show that the Spitzer approximation highly over-estimates the intensity
  of collisional attenuation of plasma waves. 

@@

  % proven 
  demonstrated when we compare it with the collisionless (Landau) damping rate. 
  In the second work to be discussed, we analyze
  the so-far ignored electrostatic bremsstrahlung effect. We show that the
  presence of electrostatic bremsstrahlung emission modifies the Langmuir
  %spectrum, which in turn alters the shape of the initial Maxwellian electron
  %velocity distribution. 
  % LFZ180220: Proposta de mudança aqui. OK?
  % Sabrina: OK
  spectrum, which in turn alters the shape of the initial electron
  velocity distribution, assumed to be Maxwellian. 
  After a long time-evolution period (numerical
  integration), the system seems to arrive to a new quasi-steady state, in
  which the shape of the electron velocity distribution resembles the shape
  of a core-halo distribution function, i.e., composed by a Maxwellian core
  and a suprathermal tail. The outcomes of both analyses are unprecedented;
  the prospects and possibilities for further studies on this subject are
  promising.
  % Sabrina: não sei se preciso mencionar este trabalho aqui, mas coloquei
  % mesmo assim. Se achares denecessário, é só comentar o trecho a seguir:
  % LFZ180220: Acho que cabe sim mencionar esse trabalho. Mas proponho uma
  % mudança na frase. Acho exagerado dizer que "não tem nenhuma relação",
  % uma vez que o bremsstrahlung é um efeito colisional.
  % Sabrina: é, eu sei que alguma relação tem, só não sabia muito como
  % expressar isso sem me enrolar. Enfim, ficou muito boa a tua sugestão. 
  In the end, we also present an extra result, indirectly related to the
  main subject of this doctoral project, regarding the analysis of the
  complete set of electromagnetic weak turbulence equations, in the presence
  of a core-halo velocity distribution function. 
  %This work, however, was a
  %parallel research and does not have any relation with the main subject of
  %this doctoral working proposal.

  % Sabrina: o trecho abaixo foi removido do abstract para dar uma
  % "enxugada" no texto. Se achares necessário, recoloco.
  % To do so, we assume Maxwellian
  % velocity distribution for ions and electrons, and consider static ions
  % while the electrons evolve in time under the quasilinear velocity diffusion
  % process, which also includes spontaneous emission, collisional damping
  % and, of course, electrostatic bremsstrahlung in the wave kinetic equation.
  % For the particles we consider the quasilinear particle kinetic equation
  % added by the linearized Landau collision operator.

@@

% LFZ180220: Coloquei espaço entre a vírgula e "Phys. Rev. E"
% Sabrina: OK

@@

% LFZ180220: Mudei para "O resultado", para combinar com "foi"
% Sabrina: Nossa, sério que eu errei isso aqui também? Geeente...
% Traduzi sem nem pensar a respeito, que vergonha.

@@

    %causado pelo espalhamento das partículas do plasma, nomeado como
% LFZ180220: Proponho mudança, compatível com a proposta no "abstract"
% Sabrina: OK

@@

    %solar. O primeiro trabalho se refere à nova equação para o amortecimento
    %colisional, no qual comparamos o resultado da integração numérica dessa
% LFZ180220: Proponho mudança similar àquela proposta no "abstract".
% Sabrina: OK

@@

    numérica dessa
    expressão, com a largamente usada \emph{fórmula de Spitzer}. Com isso
    conseguimos mostrar que a aproximação de Spitzer super-estima em muito
    a intensidade da atenuação colisional das ondas de plasma. Além disso,
% LFZ180220: Aqui o ordenamento das frase já estava adequado, e de acordo com
% a mudança proposta no "abstract". So faço uma pequena mudança no texto. OK?
    %a insignificância da taxa de amortecimento colisional se comprova quando
% Sabrina: OK
    a falta de relevância da taxa de amortecimento colisional fica
    demonstrada quando
    a comparamos com a taxa de amortecimento não colisional (de Landau).
    No segundo trabalho, nós analizamos o até então ignorado efeito de
    \emph{bremsstrahlung} eletrostático. Nó mostramos que a presença da
    emissão de \emph{bremsstrahlung} eletrostático modifica o espectro
    das ondas de Langmuir que, por sua vez, altera a forma da função de
    %distribuição inicial dos elétrons, que é Maxwelliana. Após um longo
% LFZ180220: Mudança compatível com a mudança proposta no "abstract".
% Sabrina: OK
    distribuição inicial dos elétrons, suposta Maxwelliana. Após um longo
    tempo de evolução temporal (integração numérica), o sistema parece
    chegar a um novo estado quase-estacionário, no qual a forma da função
    de distribuição de velocidades dos elétrons lembra a forma de uma função
    de distribuição núcleo-halo, ou seja, composta por um núcleo Maxwelliano e
    uma cauda supratérmica. Os resultados de ambas análises são sem precedentes;
    as perspectivas e as possibilidades para novos estudos neste assunto são
    promissoras.
    % Sabrina: não sei se preciso mencionar este trabalho aqui, mas coloquei
    % mesmo assim. Se achares denecessário, é só comentar o trecho a seguir:
% LFZ180220: Mudança proposta similar à que foi proposta no "abstract":
    %No final é também apresentado um resultado extra, relativo à
% Sabrina: OK
    No final é também apresentado um resultado extra, indiretamente relacionado
    ao assunto principal desse projeto de trabalho de doutorado, relativo à
    análise do conjunto completo de equações eletromagnéticas da teoria de
    turbulência fraca, na presença de uma função de distribuição de velocidades
    núcleo-halo. 
    %Este trabalho, no entanto, não tem relação com o assunto
    %principal dessa proposta de trabalho de doutorado.

@@

In the context of the plasma kinetic theory, processes
involving waves and kinetic instabilities, the so-called\emph{
  collective processes}, are almost exclusively associated with
situations in which the effects of collisional dissipation can
be neglected, what happens when the studied phenomenon evolves
in a much shorter time-scale than the collisional relaxation time
of the plasma in question \cite{akhi1967}. In such cases, the
plasma dynamics may be described by the Vlasov-Maxwell system, 
a complex set of coupled equations whose solution invariably will
depend on some degree of approximation. In the presence of small
amplitude oscillations in a fully ionized plasma, we can make use
of perturbation theory in order to solve such complicated system
\cite{klimo}. From this method, one may obtain simpler approximations
like the linear theory and the quasilinear formalism, and also
more complex formulations, like the weak turbulence theory, which
takes into account low-order nonlinearities on the plasma dynamics.

With the lowest order of this chain of perturbative approximations, the
linear theory, it is possible to obtain the dispersion relations, which
are mathematical expressions that not only help us on identifying the
different oscillatory modes that may be excited in plasmas, but also
wholly characterizes these oscillations. 
% LFZ180216: Como está no plural, "dispersion relations", acho que a frase
% deve seguir como:
% "mathematical expressions that not only help us on identifying the
% different oscillatory modes that may be excited in plasmas, but also
% wholly characterize these oscillations."
% Sabrina: OK
Valuable information like
how these waves propagate and the frequencies that will resonate with
the plasma particles, resulting in damping or amplification of these
% LFZ180216: "of these"?
% Sabrina: OK
oscillations \cite{bitt,chen,gurnett2017}, are given by the dispersion
relations. This information, however, is static. 
% LFZ180216: "is static", ao invés de "it is static"? Acho que o sujeiro já
% é "This information", não precisa do "it".
% Sabrina: OK
There is no way to
know, based solely on the linear formulation, any further development
of the system, how these waves will evolve in time from a given initial
state, for instance. Thus, to clarify if these oscillations will grow
until their amplitudes become too large to be treated by a perturbative
method, or if they will rapidly increase and saturate, or if they will
be completely damped, or if they will decrease a little and then saturate, 
a certain degree of nonlinearity must be taken into account. That is the
purpose of the quasilinear approximation.
% LFZ180216: Sugestão:
% "Thus, to clarify if these oscillations will grow
% until their amplitudes become too large to be treated by a perturbative
% method, or if they will rapidly increase and saturate, 
% or if they will be completely damped,
% or if they will decrease a little and then saturate, 
% a certain degree of nonlinearity must be taken
% into account. That is the purpose of the quasilinear approximation."
% Sabrina: OK

In the quasilinear theory, low-order nonlinear terms are kept in
the equation for the time evolution of the velocity distribution
function. The velocity distribution will then evolve in time
through a process of diffusion in velocity space,
% LFZ180216: Acho que não está errado, mas me parece melhor "through a
% process of diffusion in velocity space,"
% Sabrina: OK
 in which the diffusion
coefficient depends on the spectral energy density of the waves.
The dispersion relation is formally given by the same expression
obtained under the linear theory, except that now it 
depends on a time-dependent velocity distribution function, 
% LFZ180216: Suggestion: depends on a time-dependent velocity
% distribution function,
% Sabrina: OK
which must vary in a much slower
time-scale than the period of the plasma oscillations. Under such
condition, the gradual changing on the velocity space shape slowly
modifies the wave spectrum, whose new form will then alter the
velocity distribution function and so on, until a new quasi-stationary
equilibrium state is attained \cite{gurnett2017}. However, depending
on the phenomenon being described this saturation state reached
under the quasilinear approximation might keep on evolving if higher
order nonlinearities are taken into account \cite{akhi2}. This kind
of nonlinear analysis is given by the \emph{weak turbulence theory},
which is the next step in this chain of perturbative approximations.

Mostly developed in the period between the late $1950$s and early
$1970$s \cite{Kadomtsev1965,Tsytovich1967,saggal,tsynlep,david,
  tsyitotp,akhi2,tsytotp,mel}, the weak turbulence theory has
become a valuable theoretical tool for the analysis of nonlinear
phenomena in plasmas since then, being applied in several studies
until nowadays \cite{Grognard1982,McClements87b,Hanssen1991,
  Edney2001,Kontar2001,Kontar2002,THD13}. Its complex formulation
is constituted by a set of coupled kinetic equations, which describe
the time evolution of the velocity distribution functions of the
plasma particles and the time evolution of the spectral intensities of
the plasma wave modes. The development of the weak turbulence theory
was resumed in a relatively recent series of papers, where the author,
starting from first principles, has extended the original formalism in
order to include new effects. In the initial work, it was considered
only the propagation of electrostatic oscillations, 
% LFZ180216: Em lugar do trecho acima, acho melhor dizer "it was considered
% only the propagation of electrostatic oscillations,"
% Isso porque a frase anterior falava que novos efeitos tinham sido
% incluidos ao formalismo, e dessa forma o "added" parece indicar que as
% oscilações eletrostáticas foram adicionadas, como novos efeitos, e não 
% é o caso.
% Sabrina: OK
taking into account the
effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
Later, the formalism was expanded, and the effects of discrete particle,
% LFZ180216: "discrete particle effects"?
% Sabrina 20/02: acho que passei batido por esse antes...
related to spontaneous emission and spontaneous scattering processes
were included \cite{Yoon05a}. In a further extension, the effects of
the propagation of electromagnetic waves were incorporated into the
revised formulation \cite{Yoon06,Yoon2012b}.

The equations of this revised version of the weak turbulence theory
have been the subject of extensive studies involving nonlinear analysis
and two-dimensional numerical integration applied to the time evolution
of the Langmuir turbulence \cite{ZGPY08,Ziebell2012,YZGLW12,
  ZYGP14a,ZYGP14b} in a fully ionized and unmagnetized plasma, and in
other studies that also include the emission of electromagnetic waves
\cite{ZYSGP14c,ZYPGP15,ZPYGP16}. Some studies
using a one-dimensional approach have also been made 
\cite{ZiebellGY01,GaelzerZY02,GZVYR08}.
% LFZ180216: Nessa parte final da frase a ideia não era dizer "other studies
% that also include the emission of electromagnetic waves"?
%
% Sabrina: Pode ser. Acho, traduzi mal o texto do plano de pesquisa
% para o PDSE.
% LFZ180220: No plano para o PDSE havia uma frase mais ambígua do que essa que
% propus aqui. Dizia "estudo de processos de emissão envolvendo ondas de
% Langmuir". Nota que se diz "processos de emissão", sem especificar o tipo.
% E depois "envolvendo ondas de Langmuir". Não era apenas "emissão de ondas
% de Langmuir", como tinhas escrito na primeira versão. Poderíamos colocar
% a mesma frase do PDSE, mas acho que esta que diz "also include the emission
% of electromagnetic waves" também serve. A frase anterior fala em turbulência
% de Langmuir", e essa fala em "also include" outros efeitos. OK?
% Sabrina: OK
%
% LFZ180216: Outra coisa: Poderia haver aqui uma frase como "Some studies
% using a one-dimensional approach have also been made 
% \cite{ZiebellGY01,GaelzerZY02,GZVYR08}."
% Na verdade, essa referência GZVYR08, se aparecer aqui assim como sugiro, deve
% sair da frase anterior onde estão mmencionadas análises bi-dimensionais.
% Sabrina: Desculpa, mas não entendi bem como escrever essa parte, até porque
% tenho pouca familiaridade com esses trabalhos em 1D. Na verdade não tenho eles
% nem em  bibtex, nem em pdf. Mas se quiseres editar o texto para colocar eles
% e adicionar o bibtex no papers.bib, ficarei muito agradecida. Se eu for fazer
% isso, vai me tomar um tempo que infelizmente não tenho...
% LFZ180220: OK, vou fazer a mudança conforme estava proposto, e adicionar as
% referências.
% Sabrina: Obrigada!
The Langmuir turbulence is a by-product 
% LFZ180216: "by-product"?
% Sabrina: OK
of the instability generated when an energetic electron beam interacts with
a background plasma. The electron beam alters the electron velocity
distribution triggering the so-called \emph{bump-in-tail instability}.
Besides being recurrently used in textbooks as an illustrative example
of the quasilinear diffusion process \cite{akhi2,chen,gurnett2017}, the
bump-in-tail instability also has an essential role in the study of type
II and type III radio bursts \cite{Emslie1984,Hannah2009,ZVST11,Hannah2011,
  KK12,RR14,BNKR14}. In this context, the relevance of a more accurate
description of nonlinear kinetic instabilities in plasmas, represented
here by the beam-plasma interaction, becomes clear.

@@

In a recent paper \cite{YZKS16}, it was presented the first rigorous
theory that, starting from first principles, incorporates collisional
effects into the already well established weak turbulence formalism.
The authors used 
% LFZ180216: Acho que podes escrever "The authors used ..." e mais abaixo na
% frase "they also kept ...", ou então "The authors use ..., they also keep".
% Como está misturas dois tempos verbais na mesma frase.
% Sabrina: OK, corrigi para "used"
the same standard weak turbulence perturbative method
but, instead of keeping only the collective eigenmodes in the linear
and nonlinear wave-particle interactions, they also kept the effects
of the non-collective fluctuations emitted by thermal particles. The
outcome is a complete first principles nonlinear description of the
propagation of electrostatic oscillations in the presence of both wave
and particle collisional dissipation, and a hitherto unknown process.
This new effect depicts the emission of electrostatic radiation in the
eigenmode frequency range, which is caused by particle scattering. 
Since this is a form of braking radiation, 
% LFZ180216: "braking radiation"?
% Sabrina: OK
the authors named it as
\emph{electrostatic bremsstrahlung}.

Considering the context presented above, the working proposal of
this PhD Thesis is to put forward the first numerical analysis of
the new weak turbulence theory for collisional plasmas \cite{YZKS16}
and explore its applications in the solar physics scope. In
\Cref{cha:kin-theo} and \Cref{cha:weak-turb}, we make a brief review
of the basic plasma kinetic theory equations and the weak turbulence
theory, respectively. In \Cref{noneigenmode}, we introduce the
new generalization of the weak turbulence theory, which takes into
account the contribution of noneigenmode fluctuations during the
derivation of the particle and wave kinetic equations, resulting
in three new terms. In \Cref{main}, we contextualize the present
work regarding the theory discussed in the previous chapter and
present the results obtained so far by appending the two papers
published in this subject. In \Cref{cha:final}, we summarize the
results and discuss the perspectives of the present research.
Then, we propose a schedule for the remaining period 
% LFZ180216: "for the remaining period"?
% Sabrina: OK
until the thesis
defense. In the end we have three appendices. \Cref{appA} shows
an improved approximation for the second order susceptibility of
the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
presents a discussion about the asymptotic equilibrium state of the
Langmuir waves spectrum, considering a combination of a inverse
power-law kappa distribution and a Maxwellian distribution, in the
presence and in the absence of the electrostatic bremsstrahlung.
% LFZ180216: Tenho a impressão que essa última frase dá uma impressão errada.
% Se bem me lembro, é suposta a presença de uma distribuição do tipo
% "inverse power-law", mas na hora de calcular o bremsstrahlung se usa uma
% Maxwelliana. Sugiro uma frase mais ambígua, que não entra em detalhes, mas
% não diz que o bremsstrahlung foi calculado com a "Kappa". Por exemplo,
% "presents a discussion about the asymptotic equilibrium state of the
% Langmuir waves spectrum, considering a combination of a inverse power-law 
% kappa distribution and a Maxwellian distribution, in the presence and in the
% absence of the electrostatic bremsstrahlung."
% Sabrina: OK
The discussion in \Cref{appB} is
related with the article appended in \Cref{appC}, which is a
parallel research and is only slightly related with the main
subject of this work, that is the study of the combined action
of collective and collisional processes in weakly turbulent
plasmas, in the presence of electrostatic oscillations.

@@

As mentioned before, in the absence of collisions, the plasma
dynamics is given by the Vlasov-Maxwell system, which is composed
by the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{q_{\alpha}}{m_{\alpha}}
  \left({\bf E}({\bf r},t)+\frac{1}{c}{\bf v}\times {\bf B}({\bf r},t) \right)
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0,
\end{equation}
where the fields are described by the Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial \bf B}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t},
\end{eqnarray}
here given in cgs units, as commonly used in the
plasma physics literature.

>>>>

@@

@@

  damping rate for Langmuir and ion-sound waves, and the discovery of a new
  fundamental  process of emission of electrostatic fluctuations, in the
  ion-sound and Langmuir frequency range, caused by binary interactions of
  particles, named \emph{electrostatic bremsstrahlung}. In the present study
  we introduce the first numerical analysis of these two new equations and

@@

@@

  and in it we compare the results of numerical integration of the rigorous
  expression with the damping rate calculated with the widely applied
  \emph{Spitzer formula}. We show that the Spitzer approximation highly
  over-estimates the intensity of collisional attenuation of plasma waves. 

@@

  demonstrated when we compare it with the collisionless (Landau) damping
  rate. In the second work to be discussed, we analyze the so-far ignored
  electrostatic bremsstrahlung effect. We show that the presence of
  electrostatic bremsstrahlung emission modifies the Langmuir spectrum,
  which in turn alters the shape of the initial electron velocity
  distribution, assumed to be Maxwellian. After a long time-evolution period
  (numerical integration), the system seems to arrive to a new quasi-steady
  state, in which the shape of the electron velocity distribution resembles
  the shape of a core-halo distribution function, i.e., composed by a
  Maxwellian core and a suprathermal tail. The outcomes of both analyses are
  unprecedented; the prospects and possibilities for further studies on this
  subject are promising. In the end, we also present an extra result,
  indirectly related to the main subject of this doctoral project, regarding
  the analysis of the complete set of electromagnetic weak turbulence equations,
  in the presence of a core-halo velocity distribution function. 

@@

@@

@@

@@

@@

    numérica dessa expressão, com a largamente usada \emph{fórmula de Spitzer}.
    Com isso conseguimos mostrar que a aproximação de Spitzer super-estima
    em muito a intensidade da atenuação colisional das ondas de plasma. Além
    disso, a falta de relevância da taxa de amortecimento colisional fica
    demonstrada quando a comparamos com a taxa de amortecimento não colisional
    (de Landau). No segundo trabalho, nós analizamos o até então ignorado efeito
    de \emph{bremsstrahlung} eletrostático. Nó mostramos que a presença da
    emissão de \emph{bremsstrahlung} eletrostático modifica o espectro das ondas
    de Langmuir que, por sua vez, altera a forma da função de distribuição
    inicial dos elétrons, suposta Maxwelliana. Após um longo tempo de evolução
    temporal (integração numérica), o sistema parece chegar a um novo estado
    quase-estacionário, no qual a forma da função de distribuição de velocidades
    dos elétrons lembra a forma de uma função de distribuição núcleo-halo, ou
    seja, composta por um núcleo Maxwelliano e uma cauda supratérmica. Os
    resultados de ambas análises são sem precedentes; as perspectivas e as
    possibilidades para novos estudos neste assunto são promissoras. No final é
    também apresentado um resultado extra, indiretamente relacionado ao assunto
    principal desse projeto de trabalho de doutorado, relativo à análise do
    conjunto completo de equações eletromagnéticas da teoria de turbulência
    fraca, na presença de uma função de distribuição de velocidades núcleo-halo. 

@@

% In the context of physics, the word ``plasma'' is used to designate a gas whose degree
% of ionization is such that the interaction between its components is dominated by the electric
% and magnetic forces generated by the presence and movement of the negatively and positively
% charged particles.
%
% In the context of physics, the word ``plasma'' is used to designate a gas whose
% degree of ionization is such that its dynamics is dominated by the forces of
% electric and magnetic nature of the charged particles, overcoming the influence
% of the collisions between neutral particles.
%
In the context of physics, the word ``plasma'' is used to designate a gas whose
degree of ionization is such that the forces of electric and magnetic nature of
the charged particles overcome the influence of the collisions between neutral
particles, in the overall dynamics of the gas. Besides that, the

When it comes to the plasma kinetic theory, processes involving waves
and kinetic instabilities, the so-called \emph{collective processes},
are almost exclusively associated with situations in which the effects
of collisional dissipation can be neglected, what happens when the
studied phenomenon evolves in a much shorter time-scale than the
collisional relaxation time of the plasma in question \cite{akhi1967}.
In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
system, a complex set of coupled equations whose solution invariably will
depend on some degree of approximation. In the presence of small
amplitude oscillations in a fully ionized plasma, we can make use
of perturbation theory in order to solve such complicated system
\cite{klimo}. From this method, one may obtain simpler approximations
like the linear theory and the quasilinear formalism, and also
more complex formulations, like the weak turbulence theory, which
takes into account low-order nonlinearities on the plasma dynamics.

With the lowest order of this chain of perturbative approximations, the
linear theory, it is possible to obtain the dispersion relations, which
are mathematical expressions that not only help us on identifying the
different oscillatory modes that may be excited in plasmas, but also
wholly characterizes these oscillations. Valuable information like
how these waves propagate and the frequencies that will resonate with
the plasma particles, resulting in damping or amplification of these
oscillations \cite{bitt,chen,gurnett2017}, are given by the dispersion
relations. This information, however, is static. There is no way to
know, based solely on the linear formulation, any further development
of the system, how these waves will evolve in time from a given initial
state, for instance. Thus, to clarify if these oscillations will grow
until their amplitudes become too large to be treated by a perturbative
method, or if they will rapidly increase and saturate, or if they will
be completely damped, or if they will decrease a little and then saturate, 
a certain degree of nonlinearity must be taken into account. That is the
purpose of the quasilinear approximation.

In the quasilinear theory, low-order nonlinear terms are kept in
the equation for the time evolution of the velocity distribution
function. The velocity distribution will then evolve in time through
a process of diffusion in velocity space, in which the diffusion
coefficient depends on the spectral energy density of the waves.
The dispersion relation is formally given by the same expression
obtained under the linear theory, except that now it depends on a
time-dependent velocity distribution function, which must vary in a
much slower time-scale than the period of the plasma oscillations.
Under such condition, the gradual changing on the velocity space
shape slowly modifies the wave spectrum, whose new form will then
alter the velocity distribution function and so on, until a new
quasi-stationary equilibrium state is attained \cite{gurnett2017}.
However, depending on the phenomenon being described this saturation
state reached under the quasilinear approximation might keep on
evolving if higher order nonlinearities are taken into account
\cite{akhi2}. This kind of nonlinear analysis is given by the
\emph{weak turbulence theory}, which is the next step in this chain
of perturbative approximations.

Mostly developed in the period between the late $1950$s and early
$1970$s \cite{Kadomtsev1965,Tsytovich1967,saggal,tsynlep,david,
  tsyitotp,akhi2,tsytotp,mel}, the weak turbulence theory has
become a valuable theoretical tool for the analysis of nonlinear
phenomena in plasmas since then, being applied in several studies
until nowadays \cite{Grognard1982,McClements87b,Hanssen1991,
  Edney2001,Kontar2001,Kontar2002,THD13}. Its complex formulation
is constituted by a set of coupled kinetic equations, which describe
the time evolution of the velocity distribution functions of the
plasma particles and the time evolution of the spectral intensities of
the plasma wave modes. The development of the weak turbulence theory
was resumed in a relatively recent series of papers, where the author,
starting from first principles, has extended the original formalism in
order to include new effects. In the initial work, it was considered
only the propagation of electrostatic oscillations, taking into account
the effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
Later, the formalism was expanded, and the effects of discrete particle,
related to spontaneous emission and spontaneous scattering processes
were included \cite{Yoon05a}. In a further extension, the effects of
the propagation of electromagnetic waves were incorporated into the
revised formulation \cite{Yoon06,Yoon2012b}.

The equations of this revised version of the weak turbulence theory
have been the subject of extensive studies involving nonlinear analysis
and two-dimensional numerical integration applied to the time evolution
of the Langmuir turbulence \cite{ZGPY08,Ziebell2012,YZGLW12,
  ZYGP14a,ZYGP14b} in a fully ionized and unmagnetized plasma, and in
other studies that also include the emission of electromagnetic waves
\cite{ZYSGP14c,ZYPGP15,ZPYGP16}. Some studies using a one-dimensional
approach have also been made \cite{ZiebellGY01,GaelzerZY02,GZVYR08}.
The Langmuir turbulence is a by-product  of the instability generated
when an energetic electron beam interacts with a background plasma. The
electron beam alters the electron velocity distribution triggering the
so-called \emph{bump-in-tail instability}. Besides being recurrently used
in textbooks as an illustrative example of the quasilinear diffusion process
\cite{akhi2,chen,gurnett2017}, the bump-in-tail instability also has an
essential role in the study of type II and type III radio bursts
\cite{Emslie1984,Hannah2009,ZVST11,Hannah2011,KK12,RR14,BNKR14}. In this
context, the relevance of a more accurate description of nonlinear kinetic
instabilities in plasmas, represented here by the beam-plasma interaction,
becomes clear.

@@

In a recent paper \cite{YZKS16}, it was presented the first rigorous
theory that, starting from first principles, incorporates collisional
effects into the already well established weak turbulence formalism.
The authors used the same standard weak turbulence perturbative method
but, instead of keeping only the collective eigenmodes in the linear
and nonlinear wave-particle interactions, they also kept the effects
of the non-collective fluctuations emitted by thermal particles. The
outcome is a complete first principles nonlinear description of the
propagation of electrostatic oscillations in the presence of both wave
and particle collisional dissipation, and a hitherto unknown process.
This new effect depicts the emission of electrostatic radiation in the
eigenmode frequency range, which is caused by particle scattering. 
Since this is a form of braking radiation, the authors named it as
\emph{electrostatic bremsstrahlung}.

Considering the context presented above, the working proposal of
this PhD Thesis is to put forward the first numerical analysis of
the new weak turbulence theory for collisional plasmas \cite{YZKS16}
and explore its applications in the solar physics scope. In
\Cref{cha:kin-theo} and \Cref{cha:weak-turb}, we make a brief review
of the basic plasma kinetic theory equations and the weak turbulence
theory, respectively. In \Cref{noneigenmode}, we introduce the
new generalization of the weak turbulence theory, which takes into
account the contribution of noneigenmode fluctuations during the
derivation of the particle and wave kinetic equations, resulting
in three new terms. In \Cref{main}, we contextualize the present
work regarding the theory discussed in the previous chapter and
present the results obtained so far by appending the two papers
published in this subject. In \Cref{cha:final}, we summarize the
results and discuss the perspectives of the present research. Then,
we propose a schedule for the remaining period until the thesis
defense. In the end we have three appendices. \Cref{appA} shows
an improved approximation for the second order susceptibility of
the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
presents a discussion about the asymptotic equilibrium state of the
Langmuir waves spectrum, considering a combination of a inverse
power-law kappa distribution and a Maxwellian distribution, in the
presence and in the absence of the electrostatic bremsstrahlung.
The discussion in \Cref{appB} is related with the article appended
in \Cref{appC}, which is a parallel research and is only slightly
related with the main subject of this work, that is the study of the
combined action of collective and collisional processes in weakly
turbulent plasmas, in the presence of electrostatic oscillations.

@@

As mentioned before, in the absence of collisions, the plasma
dynamics is given by the Vlasov-Maxwell system, which is composed
by the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{q_{\alpha}}{m_{\alpha}}
  \left({\bf E}({\bf r},t)+\frac{1}{c}{\bf v}\times {\bf B}({\bf r},t) \right)
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0,
\end{equation}
where the fields are described by the Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial {\bf B}}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t},
\end{eqnarray}
here given in cgs units, as commonly used in the
plasma physics literature.
